Curiosity-driven Exploration of Skill Hierarchies

### 2015-11-05 paper1/paper.tex
xp1 xp2

@@

	See Fig. \ref{env} for the initial state of the environment.

>>>>

	We simulate a 2D robotic arm using tools to push an object in its environment with the help of an experienced pair. 
	The agent can either try to push objects into boxes on its own, or produce a vocal signal that might engage the experienced pair to help move the object to reach a box.

	The environment is designed such that each box is more easily reached by one different mean.
	Box 1 is best reached with the small stick, box 2 with the long stick, and box 3 with the small stick and the help of the pair.

	An iteration consists of the evaluation of a motor command given by the agent which gives
	sensory information back to him, and 
	finally the environment is resetted to its intial state.

@@

	The next sections precisely describe the different items of the environment and their interactions.	
	See Fig. \ref{env} for an exemple of the state of the environment.

	\subsection{Robotic arm}

		The 2D robotic arm has 3 joints plus a gripper located at the end-effector.
		Each joint can rotate from $-\pi~rad$ to $\pi~rad$ around its initial position, mapped to a standard interval of $[-1,1]$.
		The length of the 3 parts of the arm are $0.5$, $0.3$ and $0.2$ so the total length of the arm is $1$ unit.
		The initial position of the arm is vertical with each joint at $0~rad$ and its base is fixed at position $[0, 0]$.
		The gripper $g$ has 2 possible positions: \textit{open} ($g \geq 0$) and \textit{closed} ($g < 0$) and its initial position is \textit{open} (with $g = 0$).
		The robotic arm thus has 4 degrees of freedom represented by a vector in $[-1,1]^4$.
		A trajectory of the arm will be represented as a sequence of such vectors.

	\subsection{Objects and tools}

		A yellow squared object can be moved into one of the 3 fixed squared boxes. 
		The initial position of the yellow square is $(-0.75, 1)$ and is thus unreachable with directly with the gripper.
		One of 2 sticks can be grasped in order to reach the object.
		A small stick of length $0.5$ is located on the left of the arm, with initial position $(-0.5, 0)$ and initial angle $\frac{3\pi}{4}$ from the horizontal line.
		A long stick of length $1.$ is located on the right of the arm, with initial position $(0.5, 0)$ and initial angle $\frac{\pi}{4}$ from the horizontal line as in Fig. \ref{env}.

		If the gripper closes near the end of one of the sticks (closer than $0.2$), it is considered grasped and will follow the gripper's position and the angle (with some noise) of the arm's last part until the gripper opens.
		The grasped stick will have its angle equal to arm's last part plus a gaussian noise (of size $0.02$ for the small sitck and $0.1$ for the long one), updated at each step of the movement.

		Similarly, if the other end of a stick reaches the yellow squared object (within $0.25$), the object will follow the end of the stick.
		Three boxes are fixed at positions $(-1.25, 0)$, $(0, 1.75)$ and $(-1.75, 0)$ and have size $0.5$.
		At the end of the trial, the object is considered to be in one of the box if its center is in the box.

	\subsection{Help from an experienced pair}

		A pair sitting at the right of the robot will help him put the yellow square into the closer box.
		It will wait for the robot to move the object on its own, and if the robot also produces the good vocal signal, will move the object to the closest box.

		However, as the long stick is long enough to reach the any of the 3 boxes but not the small one, the pair will help the robot only when it will use the small stick.
		Also, as the pair is sitting on the right side of the robot, it will be unable to help reach box 1 (on the left).
		The pair will help reach box 2 (on the front) but with a bad precision as it is far, and box 3 (on the right) with a good precision.
		The pair will put the object at the center of box 2 (with a gaussian noise of size $0.2$ on x and y dimensions thus missing the box quite often), 
		only if the object is located near box 2 at a distance from the base of the arm greater than $1.$ and an angle from the horizontal line between $45°$ and $105°$.
		If the angle is between $-15°$ and $45°$, then the pair moves it towards the center of box 3 with a gaussian noise of size $0.05$, thus rarely missing the box.

		We simulate a simple vocal signal controled by pitch and intensity between $-1$ and $1$.
		The pair will engage in helping the robot only if pitch and intensity were sufficiently high ($>0.$).
	%

	\subsection{Motor control}

		We use Dynamical Movement Primitive \cite{ijspeert_dynamical_2013} to control the arm's movement as this framework permits the production of a diversity of arm's trajectories with few parameters.
		Each of the 4 arm's degree of freedom (DOF) is controlled by a DMP with a starting and a goal position equal to the rest position of the joint.
		Each DMP is parameterized by one weight on each of 3 basis functions whose centers are distributed homogeneously throughout the movement.
		The weights are bounded in the interval $[-200,200]$ (mapped to the standard interval $[-1,1]$) which allow each joint to cover its standard interval $[-1,1]$ during the movement.
		Each DMP outputs a series of $50$ positions that represents a sampling of the trajectory of one joint during the movement.

		The arm's movement is thus parameterized by $12$ weights, and the static vocal signal by $2$ weights.
		Let $M_a$ be the $12D$ space of arm's commands $[-1,1]^{12}$, $M_v$ be the $2D$ vocal space, and $M$ the $14D$ global motor space.

	\subsection{Sensory feedback}

		At the end of the movement, the robot gets sensory feedback from the different items of the environment.
		It gets the trajectory of its hand and gripper, whether the vocal signal engaged the pair or not, the trajectory of the end of the sticks, 
		the end position of the object, and whether the object is in each box and at which distance.

		The trajectory of the hand and of the end point of the sticks is the sequence of x and y positions at different time points: steps $12$, $25$, $37$ during the movement of $50$ steps.
		The trajectory of the gripper is a sequence of $1$ or $-1$ depending whether the gripper is open or not.
		The pair understanding of the vocal signal is represented as $1$ if intensity and pitch were correct, $-1$ otherwise.
		For each box, the robot receives a $1$ if the object was in the box, and $0$ otherwise, plus the distance between the end position of the object and the center of the box.

		The sensory information thus contains $6$ dimensions for the trajectory of the hand, $1$ for the pair help, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object, and $2$ for each box.
		The total sensory space has $44$ dimensions.
